---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SurveyLand: an R Shiny application to streamline the analysis and reporting of complex survey data

*SurveyLand* is an R Shiny application developed by the Division of Research and Methodology at the National Center for Health Statistics (NCHS) to improve the efficiency, transparency, and reproducibility of survey data workflows, while making insights more accessible. It provides a user-friendly, stepwise workflow for preparing survey data, specifying complex survey design features, generating tables and plots, and exporting presentation-ready outputs aligned with NCHS data presentation standards. 

Although *SurveyLand* can be used with a wide range of datasets, it's designed to support the unique requirements of complex survey data analysis, including clustering, stratification, and weighting. It is intended for users who need design-based estimates and:

  - outputs aligned with NCHS data presentation standards
  - quick export to Word, Excel, or image formats
  - a guided interface for preparing and analyzing data

> This project is still in development. Features and documentation are subject to change.

## Features

### Data ingestion and preparation

**Supported file formats**

| Format | Extension(s) |
|---|---|
| Comma-separated values | `.csv` |
| Excel | `.xlsx`, `.xls` |
| SAS | `.sas7bdat` |
| SPSS | `.sav` |
| R data | `.RData`, `.rdata`, `.Rda`, `.rda`, `.rds`, `.RDS`, `.Rds` |

Files up to 300 MB are supported.

**Survey metadata** 
Enter metadata that auto-populates table titles, figure titles, and data source captions, including: data producer, survey name, survey round or cycle, field dates, and geographic area.

**Data filtering**
Filter by up to two variables before analysis. Users are warned not to pre-filter for subgroup analyses when using complex survey design features, as doing so can produce incorrect standard errors.

**Survey design information** 
Specify cluster/PSU, strata, and weight variables, if applicable. The application checks for missing values in selected design variables and warns when inputs are incomplete.

### Data analysis

Three analysis types are supported:

| Type | Description |
|---|---|
| **One-way** (single-variable) | Distribution for a single outcome variable |
| **Two-way** (bi-variable) | Cross-tabulation of an outcome variable by a covariate |
| **Multivariable** | Distributions across multiple variables sharing the same response options |

### Tables

- Generate tabulated, formatted, and rounded survey estimates for one-way, two-way, and multivariable analyses as `flextable` objects
- Optional suppression of low-precision estimates per NCHS data presentation standards via the [`surveytable`](https://cdcgov.github.io/surveytable/) package, which implements the methods described in [Parker et al. (2017)](https://www.cdc.gov/nchs/data/series/sr_02/sr02_175.pdf) and [Parker et al. (2023)](https://doi.org/10.15620/cdc:124368)
- Export options: PNG image, Word document (`.docx`), Excel workbook (`.xlsx`)

### Plots

- Generate bar charts for one-way, two-way, and multivariable analyses
- Customization options:
  - Value labels on bars
  - Multiple `ggplot2` themes, and a custom NCHS-style theme
  - Titles, subtitles, captions, axis labels, and legend labels
  - Axis orientation (horizontal/vertical) and bar style (stacked or side-by-side)
- Export option: PNG image

### Report generation

- Render a formatted Word document report using Quarto
- Add selected plots and survey metadata to the report for download

## Workflow

1. Upload a supported data file
2. Enter survey metadata for titles and data source captions
3. Optionally filter the dataset
4. Specify survey design and weighting variables
5. Choose an analysis type
6. Generate tables and/or plots
7. Export outputs or add plots to a report
8. Render and download the report

## Getting Started

### Prerequisites

**1. Install Quarto CLI**

Report generation requires the [Quarto command-line tools](https://quarto.org/docs/get-started/). Download and install before running the application.

**2. Install R packages**

```{r eval=FALSE}
install.packages(c(
  "shiny", "shinyFeedback", "shinyjs",           # Shiny and UI utilities
  "haven", "readxl",                             # Data import
  "tidyverse", "glue", "sjlabelled", "labelled", # Data wrangling
  "survey", "srvyr", "surveytable",              # Survey analysis
  "DT", "flextable",                             # Tables and visualization
  "quarto", "officer", "openxlsx"                # Export and reporting
))
```

### Running the App

If `app.R` is in your working directory, launch the application with:

```{r eval=FALSE}
shiny::runApp("app.R")
```

Alternatively, open `app.R` in RStudio and click **Run App**.

Once launched, click the **User Guide** button for step-by-step instructions. This requires that `docs/user-guide.html` exists in the expected location.

## File Structure

The files below are required for full functionality:

```
├── app.R                 # Main Shiny application
├── report.qmd            # Quarto template for Word report generation
├── docs/
│   └── user-guide.html   # HTML user guide for the in-app modal 
└── README.md
```

> Depending on your repository layout, `app.R` may be in a subfolder such as `scripts/shiny/`.

## Pilot Use

*SurveyLand* was piloted using data from the NCHS [Research and Development Survey (RANDS)](https://www.cdc.gov/nchs/rands/index.html), a survey that employs a complex design incorporating both probability and non-probability samples.

## Troubleshooting

**Report generation fails**  
Report generation fails if Quarto CLI has not been installed. Download it from [quarto.org](https://quarto.org/docs/get-started/) and restart your R session. Also, check that `report.qmd` exists in the expected location.

**Missing values warning on design variables**  
The application checks for `NA` values in your cluster, strata, and weight variables. Use the filtering step to remove incomplete cases before creating the survey design object.

**File upload fails**  
Files must be under 300 MB and in a supported format (see [Supported file formats](#data-ingestion-and-preparation)). Very large files may take a moment to load.

**Multivariable analysis warning: "variables do not have identical response options"**
Selected variables for multivariable analysis should share the same response options. Check that the variables are consistent.

**User Guide does not open**
Check that `docs/user-guide.html` exists in the expected location.

## Authors and Acknowledgements

**Authors**

- Kristen Cibelli Hibben, CDC/NCHS/DRM/CCQDER (kcibelli\@cdc.gov)
- Sarah Forrest, CDC/NCHS/DRM/OD (sforrest\@cdc.gov)
- Paul Scanlon (former CDC)
- Zachary Smith (former CDC)

**Organization:** CDC / NCHS / DRM

**Acknowledgements**

- CDC Data Science Upskilling (DSU) Program
- Alex Strashny (author of [`surveytable`](https://cdcgov.github.io/surveytable/))

## Citation
	
If you use *SurveyLand* in your research, please include the following statement in the Methods section of your article or report:
	
> Data analyses were performed using the R Shiny application "SurveyLand."
	
Please cite this software as follows:
	
> Cibelli Hibben K, Forrest S, Scanlon P, Smith Z (2026). *SurveyLand: An R Shiny application to streamline the analysis and reporting of complex survey data*. National Center for Health Statistics. <https://github.com/CDCgov/SurveyLand>.
